### 2016-08-15 latex/paper.tex
Rim strain energy

The first page begins with the title of the paper, the authors, affiliations, 
abstract and keywords as it is shown in this document. The title of the paper 
should be typed in 14\,pt bold font and be centred. It should be separated 
from the symposium name by a 12\,pt space and from authors' names by an 18\,pt 
space. Authors' names should be typed in bold font. Affiliations should be 
typed in a general formatting style, centred within a corresponding bounding 
box. The abstract part of the final paper should not be longer than about 
300~words, so it fits on the title page. The abstract begins with the 
``ABSTRACT'' header typed in bold 11\,pt font. The abstract text should be 
separated from the header by an 11\,pt space. The abstract should be followed 
by a list of keywords after the header ``Keywords:'' typed in bold 11\,pt 
font. The keywords should be separated by commas. A dot should be place after 
the last keyword. Up to about five keywords are allowed. Title, affiliations, 
abstract and keywords have to fit on the title page. The Introduction 
paragraph may start already on the title page provided there is enough space.

@@

The rim is modeled as an initially circular beam with a constant cross-section.

>>>>

@@

The rim is modeled as an initially circular beam with a constant cross-section. For simplicity we will assume that the shear center and centroid of the cross-section coincide. Except for warping deformation, plane cross-sections remain planar and shear flexibility of the cross-section is neglected. Furthermore, we assume that the rim radius is much larger than the height of the rim profile.

The in-plane curvature of the rim is $\kappa_2 = 1/R$ and remains constant during flexural-torsional buckling. The out-of-plane curvature and axial twist rate are
\begin{equation}\label{eq:k2}
\kappa_2 = u'' - \frac{\phi}{R}
\end{equation}
\begin{equation}\label{eq:k3}
\kappa_3 = \phi' + \frac{1}{R} u'
\end{equation}
The symbol $()'$ indicates a derivative with respect to $s$. It can easily be verified that Equations \ref{eq:k2} and \ref{eq:k3} simplify to the standard equations for straight beams in the limit $R\rightarrow \infty$. The curvature and twist rate produce a bending moment and twisting moment equal to
\begin{equation}\label{eq:M2}
M_2 = EI_{11} \kappa_2
\end{equation}
\begin{equation}\label{eq:M3}
M_3 = GJ \kappa_3 + EI_w \kappa_3''
\end{equation}
The strain energy is decomposed into lateral bending, uniform torsion, and warping terms which are related to the curvatures.
\begin{equation}\label{eq:Urim}
U_{rim} = \frac{1}{2} EI_{22} \kappa_2^2 + \frac{1}{2} GJ \kappa_3^2 + \frac{1}{2} EI_w (\kappa_3')^2
\end{equation}
